---
title: "ESM 206 - Lab 8"
author: "Karina Johnston"
date: "11/15/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attach packages
library(tidyverse)
library(here)
library(broom)
library(corrplot)
library(stargazer)
library(modelsummary)
```

Contains housing price information for 780 homes on central coast of CA.

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

remember use unique function to view specific column variables

```{r}
unique(homes$City)
```

a little bit of cleaning: make a subset of homes, where city is SLO, Arroyo Grande, Atascadero, Santa Maria-Orcutt 

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("Arroyo Grande", "San Luis Obispo", "Atascadero", "Santa Maria-Orcutt"))
```

## do a little exploring...

summary statistics for home price based on city and sale status:

mean and SD for home price, grouped by city and sale status

```{r}
summary_table <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE), 
            sd_price = sd(Price, na.rm = TRUE))
summary_table

# actually, I don't want to run this code when it knits - it's just for me
# use "eval = FALSE" in the code header!

# guideline for within aes is if it is referring to a variable!  If referring to a constant, then outside aes
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  theme_classic() +
  scale_x_continuous(limits = c(0, 3e6))
```

explore the relationship between square footage and home price
change point COLOR by city and SHAPE by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status)) +
  theme_classic() +
  geom_smooth(method = lm)
```

